Hypothesis tests for multiple responses regression models in \proglang{R}: The \pkg{htmcglm} Package

### 2022-08-04 5_artigos/journal-of-statistical-software/draft/2-draft2/draft-jss-lineu.tex
atualiza repo

Following the ideas of \textbf{REF MEU ARTIGO}, let $\boldsymbol{\theta^{*}}$ be a $h \times 1$ vector of parameters disregarding the correlation parameters and $J^{\boldsymbol{*}-1}$ the corresponding inverse of the Godambe information matrix. Let $\boldsymbol{L}$ be a $s \times h$ hypotheses specification matrix and $\boldsymbol{c}$ a $s \times 1$ vector with the values under the null hypothesis. In this notation, $s$ represents the number of restrictions. The hypotheses to be tested can be written as:

@@

\textbf{REF MEU ARTIGO} presents examples of how to test different types of hypotheses of interest that arise in practical contexts. In this article, we shall present two examples: hypotheses for multiple parameters and hypotheses considering regression or dispersion parameters for responses under the same linear predictor.

@@

Based on the Wald statistics adapted for McGLMs, \textbf{REF MEU ARTIGO} proposed three different procedures for generating ANOVA and MANOVA tables for regression parameters, and a procedure similar to ANOVA and MANOVA to evaluate the dispersion parameters of a model. In the case of ANOVAs, a table is generated for each response variable. For MANOVAs only one table is generated, therefore, in order to be able to perform MANOVAs, the responses must be subject to the same linear predictor.

@@

The type II analysis of variance described in \textbf{REF MEU ARTIGO} tests, on each line, whether the complete model differs from the model without a variable. If there are interactions in the model, the complete model is tested against the model without the main effect and any interaction effect involving the variable. In this way, the effect of that variable on the complete model becomes better interpretable, that is, the impact on the quality of the model if we removed a certain variable. Considering the following linear predictor, the type II analysis of variance would do the following tests:

@@

The functions \code{mc_anova_I()}, \code{mc_anova_II()} and \code{mc_anova_III()} are functions designed to evaluate regression parameters; they generate analysis of variance tables per response for an object of the \code{mcglm} class. The functions \code{mc_manova_I()}, \code{mc_manova_II()} and \code{mc_manova_III()} are also functions designed to evaluate the regression parameters of the model; they generate multivariate analysis of variance tables for a McGLM where the responses are subject to the same predictor. While univariate analysis of variance functions aim to assess the effect of variables for each response, multivariate ones aim to assess the effect of explanatory variables on all response variables simultaneously. The nomenclatures follow what is presented in \textbf{REF MY ARTICLE} and the functions receive as an argument only the object that stores the fitted model.

>>>>

Following the ideas of \citet{htmcglm_proposta}, let $\boldsymbol{\theta^{*}}$ be a $h \times 1$ vector of parameters disregarding the correlation parameters and $J^{\boldsymbol{*}-1}$ the corresponding inverse of the Godambe information matrix. Let $\boldsymbol{L}$ be a $s \times h$ hypotheses specification matrix and $\boldsymbol{c}$ a $s \times 1$ vector with the values under the null hypothesis. In this notation, $s$ represents the number of restrictions. The hypotheses to be tested can be written as:

@@

\citet{htmcglm_proposta} presents examples of how to test different types of hypotheses of interest that arise in practical contexts. In this article, we shall present two examples: hypotheses for multiple parameters and hypotheses considering regression or dispersion parameters for responses under the same linear predictor.

@@

Based on the Wald statistics adapted for McGLMs, \citet{htmcglm_proposta} proposed three different procedures for generating ANOVA and MANOVA tables for regression parameters, and a procedure similar to ANOVA and MANOVA to evaluate the dispersion parameters of a model. In the case of ANOVAs, a table is generated for each response variable. For MANOVAs only one table is generated, therefore, in order to be able to perform MANOVAs, the responses must be subject to the same linear predictor.

@@

The type II analysis of variance described in \citet{htmcglm_proposta} tests, on each line, whether the complete model differs from the model without a variable. If there are interactions in the model, the complete model is tested against the model without the main effect and any interaction effect involving the variable. In this way, the effect of that variable on the complete model becomes better interpretable, that is, the impact on the quality of the model if we removed a certain variable. Considering the following linear predictor, the type II analysis of variance would do the following tests:

@@

The functions \code{mc_anova_I()}, \code{mc_anova_II()} and \code{mc_anova_III()} are functions designed to evaluate regression parameters; they generate analysis of variance tables per response for an object of the \code{mcglm} class. The functions \code{mc_manova_I()}, \code{mc_manova_II()} and \code{mc_manova_III()} are also functions designed to evaluate the regression parameters of the model; they generate multivariate analysis of variance tables for a McGLM where the responses are subject to the same predictor. While univariate analysis of variance functions aim to assess the effect of variables for each response, multivariate ones aim to assess the effect of explanatory variables on all response variables simultaneously. The nomenclatures follow what is presented in \citet{htmcglm_proposta} and the functions receive as an argument only the object that stores the fitted model.
